System's Perspective
A description and illustration of the:

* Design of your ITU-MiniTwit systems V/L/S               (L)
* Architecture of your ITU-MiniTwit systems V/L/S         (S)
* All dependencies of your ITU-MiniTwit systems on all levels of abstraction and development stages.
    That is, list and briefly describe all technologies and tools you applied and depend on. V/L/S  (v)
* Important interactions of subsystems V/L/S       (V)
*Describe the current state of your systems, for example using     results of static analysis and quality assessment systems.   D
* Finally, describe briefly, if the license that you have chosen for your project is actually compatible with the licenses of all your direct dependencies.  V

Double check that for all the weekly tasks (those listed in the schedule) you include the corresponding information.   

MSc students remember to argue for the choice of technologies and decisions for at least all cases for which we asked you to do so in the tasks at the end of each session.  L/D/F



Process' perspective
A description and illustration of:

* How do you interact as developers?     D   
* How is the team organized?          S 
* A complete description of stages and tools included in the CI/CD chains.
    That is, including deployment and release of your systems.    L/F   
* Organization of your repositor(ies).
    That is, either the structure of of mono-repository or organization of artifacts across repositories.
    In essence, it has to be be clear what is stored where and why. 
* Applied branching strategy. D
* Applied development process and tools supporting it
    For example, how did you use issues, Kanban boards, etc. to organize open tasks     D
* How do you monitor your systems and what precisely do you monitor?    F
* What do you log in your systems and how do you aggregate logs?        F
* Brief results of the security assessment.                             D
* Applied strategy for scaling and load balancing.                      F